\documentclass[10pt]{amsart}
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{eucal}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=red, citecolor = blue]{hyperref}
\usepackage[margin=2.5cm]{geometry}
\setlength{\marginparwidth}{2cm}

\usepackage[nameinlink,capitalise,noabbrev]{cleveref}

\usepackage[textwidth=2cm, textsize=small, colorinlistoftodos]{todonotes}

\newcommand{\lA}{\mathcal{A}}
\newcommand{\bA}{\mathbb{A}}
\newcommand{\lB}{\mathcal{B}}
\newcommand{\lC}{\mathcal{C}}
\newcommand{\rC}{\mathscr{C}}
\newcommand{\bC}{\mathbb{C}}
\newcommand{\lD}{\mathcal{D}}
\newcommand{\lE}{\mathcal{E}}
\newcommand{\lF}{\mathcal{F}}
\newcommand{\lG}{\mathcal{G}}
\newcommand{\lH}{\mathcal{H}}
\newcommand{\mH}{\mathrm{H}}
\newcommand{\lI}{\mathcal{I}}
\newcommand{\lJ}{\mathcal{J}}
\newcommand{\lK}{\mathcal{K}}
\newcommand{\lL}{\mathcal{L}}
\newcommand{\mL}{\mathrm{L}}
\newcommand{\lM}{\mathcal{M}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\mN}{\mathrm{N}}
\newcommand{\lN}{\mathcal{N}}
\newcommand{\fO}{\mathbf{O}}
\newcommand{\rO}{\mathscr{O}}
\newcommand{\lO}{\mathcal{O}}
\newcommand{\lP}{\mathcal{P}}
\newcommand{\bQ}{\mathbb{Q}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\mR}{\mathrm{R}}
\newcommand{\lR}{\mathcal{R}}
\newcommand{\lS}{\mathcal{S}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\lT}{\mathcal{T}}
\newcommand{\lU}{\mathcal{U}}
\newcommand{\lV}{\mathcal{V}}
\newcommand{\lX}{\mathcal{X}}
\newcommand{\lY}{\mathcal{Y}}
\newcommand{\bZ}{\mathbb{Z}}

\newcommand{\op}{\mathrm{op}} % opposite
\newcommand{\Hom}{\lH\mathrm{om}} % enriched hom-spaces, hom-spectrum
\renewcommand{\hom}{\mathrm{Hom}} % hom-set, hom-space
\newcommand{\Ho}{\mathrm{Ho}} % homotopy category
\newcommand{\set}{\lS\mathrm{et}} % category of sets
\newcommand{\Sp}{\lS\mathrm{p}} % category of spectra
\newcommand{\PSp}{\lP\Sp} % category of pre-spectra
\newcommand{\Ch}{\lC\mathrm{h}} % category of chain complexes
\newcommand{\cat}{\lC\mathrm{at}} % category of categories
\newcommand{\scat}{\mathrm{s}\cat} % category of simplicial categories
\newcommand{\sset}{\mathrm{s}\set} % category of simplicial sets
\newcommand{\Fun}{\lF\mathrm{un}} % category of functors
\newcommand{\Top}{\lT\op} % category of topological spaces 
\newcommand{\Grpd}{\lG\mathrm{rpd}} % category of groupoids
\newcommand{\Kan}{\lK\mathrm{an}} % category of Kan complexes
\newcommand{\Mod}{\lM\mathrm{od}} % category of modules
\newcommand{\Ab}{\lA\mathrm{b}} % category of abelian groups
\newcommand{\Open}{\lO\mathrm{pen}} % category of open subspaces
\newcommand{\BDelta}{\mathbf{\Delta}} % simplex category
\newcommand{\Sing}{\mathrm{Sing}} % singular simplicial set 
\newcommand{\Path}{\mathrm{Path}} % path 


\DeclareMathOperator*\colim{colim} % colimit

\newcommand{\bbefamily}{\fontencoding{U}\fontfamily{bbold}\selectfont}
\newcommand{\textbbe}[1]{{\bbefamily #1}}
\DeclareMathAlphabet{\mathbbe}{U}{bbold}{m}{n}

\def\DDelta{{\mathbbe{\Delta}}}
\newcommand{\DD}{\DDelta}

\newcommand{\adjun}[4]{
\begin{tikzcd}[row sep=0.5in, column sep=0.5in]
 #1  \arrow[r, shift left=1.8, "#3"] \pgfmatrixnextcell
 #2 \arrow[l, shift left=1.6, "#4", "\bot"'] 
\end{tikzcd}
}

\newcommand{\simpset}[7]{
 \begin{tikzcd}[row sep=0.5in, column sep=0.5in]
   #1 \arrow[r, shorten >=1ex,shorten <=1ex]
   \pgfmatrixnextcell #2 
   \arrow[l, shift left=1.2, "#5"] \arrow[l, shift right=1.2, "#4"'] 
   \arrow[r, shift right, shorten >=1ex,shorten <=1ex ] \arrow[r, shift left, shorten >=1ex,shorten <=1ex] 
   \pgfmatrixnextcell #3 
   \arrow[l] \arrow[l, shift left=2, "#7"] \arrow[l, shift right=2, "#6 "'] 
   \arrow[r, shorten >=1ex,shorten <=1ex] \arrow[r, shift left=2, shorten >=1ex,shorten <=1ex] \arrow[r, shift right=2, 
   shorten >=1ex,shorten <=1ex]
   \pgfmatrixnextcell \cdots 
   \arrow[l, shift right=1] \arrow[l, shift left=1] \arrow[l, shift right=3] \arrow[l, shift left=3] 
 \end{tikzcd}
}


%% N.R. notes
\newcommand{\nrnote}[1]{\todo[color=green!40,linecolor=green!40!black,size=\tiny]{#1}}
\newcommand{\nrmpar}[1]{\todo[noline,color=green!40,linecolor=green!40!black,
  size=\tiny]{#1}}
\newcommand{\nrnoteil}[1]{\ \todo[inline,color=green!40,linecolor=green!40!black,size=\normalsize]{#1}}

\newtheorem{theorem}[equation]{Theorem}
\newtheorem{lemma}[equation]{Lemma}
\newtheorem{proposition}[equation]{Proposition}
\newtheorem{corollary}[equation]{Corollary}
% \newtheorem{statement}[section]{Statement}

\theoremstyle{definition}
\newtheorem{definition}[equation]{Definition}
\newtheorem{example}[equation]{Example}
% \newtheorem{attone}[equation]{Attention}

\theoremstyle{remark}
\newtheorem{remark}[equation]{Remark}
% \newtheorem{intone}[equation]{Intuition}
\newtheorem{notation}[equation]{Notation}
% \newtheorem{queone}[equation]{Question}
% \newtheorem{conjone}[equation]{Conjecture}
\newtheorem{warning}[equation]{Warning}

\title{Differential Cohomology Seminar 2}
\date{06.05.2025 $\&$ 13.05.2025}
\author{Talk by Matthias Frerichs}

\numberwithin{equation}{section}

\begin{document}
\maketitle

In this lecture we want to learn the basics of $\infty$-category theory. For the $\infty$-categorical background, we broadly follow \cite{groth2010inftycats} and a little \cite{lurie2009htt}.

\section{Basics on \texorpdfstring{$(\infty,1)$}{(oo,1)}-categories}

There are a pletora of models for $\infty$-categories, here we focus on two. The first of such models, \emph{quasi-categories}, requires a bit of background on simplicial sets, which we recall now. 
\begin{definition}
  Given a natural number $n$, denote by $\langle n\rangle$ the partially ordered set $\{0,\cdots,n\}$. The \emph{simplex category} $\BDelta$ is the category of finite linerly ordered sets of the form $\langle n\rangle$, for any $n$, and monotone functions.
\end{definition}
We single out two classes of functions in $\BDelta$: 
\begin{definition}
  Given $0\leq i\leq n$, the \emph{$i$-coface map} is the unique injective monotone function $\delta^i_n:\langle n-1\rangle\to\langle n\rangle$ such that $i$ does not belong in the image of $\delta^i_n$. The \emph{$i$-codegeneracy map} is the unique surjective monotone function $\sigma^i_n:\langle n+1\rangle\to\langle n\rangle$ such that $i$ and $i+1$ have the same image. 
\end{definition}
\begin{theorem}[{\cite[I.4]{goerssjardine1999simplicialhomotopytheory}}]
  As a category, $\BDelta$ is generated from the face and degeneracy maps subject to the \emph{simplicial identities}. 
\end{theorem}
\begin{definition}
  A \emph{simplicial set} is a contravariant functor $X:\BDelta^{\op} \to \set$. The category of simplicial sets is denoted by $\sset$. An element of $X_n=X(\langle n\rangle)$ is called a \emph{$n$-simplex}. The function $X_n\to X_{n-1}$, resp $X_n\to X_{n+1}$, induced by $\delta^i_n$, resp. $X(\sigma^i_n)$, is called the \emph{$i$-face map}, resp. \emph{$i$-degeneracy map}, and denoted $d^n_i$, resp. $s^n_i$. 
\end{definition}
A simplicial set can be depicted as follows: 
\begin{equation}
\simpset{X_0}{X_1}{X_2}{}{}{}{}  
\end{equation}
\begin{definition}
  Given $0\leq i\leq n$, the \emph{$i$-horn} is the simplicial sub-set $\Lambda^n_i\subseteq\Delta^n$ defined as follows: A monotone map $f:\langle k\rangle\to\langle n\rangle$ is a $k$-simplex of $\Lambda^n_i$ if there is $j\neq i$ that does not belong in the image of $f$. A horn $\Lambda^n_i$ is \emph{inner} if $0<i<n$. 
\end{definition}
\begin{definition}A simplicial set $X$ is called a \emph{$\infty$-category} if, for every $n$ and $0<i<n$, every map of simplicial sets $\Lambda^n_i\to X$ admits an extension to a map $\Delta^n\to X$. If the condition is verified for every $n$ and $0\leq i\leq n$, $X$ is called a \emph{$\infty$-groupoid}.
\end{definition}
\begin{remark}
  A map of simplicial sets $f:X\to Y$ is called a \emph{Kan fibration} if it has the \emph{horn lifting property}: For every $n$ and every $0\leq i\leq n$, every diagram \begin{equation}
    \begin{tikzcd}
      \Lambda^i_n \arrow[r] \arrow[d] & X \arrow[d,"f"] \\
      \Delta^n \arrow[ru,dashed] \arrow[r] & Y
    \end{tikzcd}
  \end{equation}admits a dashed arrow making both triangles commute. A map $f$ is a \emph{inner Kan fibration} if the horn lifting property holds only for inner horns, i. e. $0<i<n$. A simplicial set $X$ is a $\infty$-groupoid, resp. $\infty$-category, if and only if the terminal map $X\to\Delta^0$ is a Kan fibration, resp. inner Kan fibration. 
\end{remark}
\begin{definition}
  Given a category $\lC$, its \emph{nerve} is the simplicial set $\mN\lC$ defined as follows: For $n\geq1$, a $n$-simplex of $\mN\lC$ consists of a $n$-tuple of composable arrows. The objects of $\lC$ are the $0$-simplices. 
\end{definition}
\begin{proposition}
  $\mN\lC$ is a $\infty$-category. 
\end{proposition}
Viewed as a functor from categories to $\infty$-categories, the nerve functor admits a left adjoint called the \emph{homotopy category} functor $\Ho$. We will sketch the construction of $\Ho X$, refering to \cite{land2021introduction} and \cite{groth2010inftycats} for more details. 
\begin{remark}
  Given a 1-simplex $f$, we write $f:x\to y$ to mean that $d^1_1(f)=x$ and $d^1_0(f)=y$. The 1-simplex $s^0_0(x)$ is written as \begin{equation}
    \begin{tikzcd}
      x \arrow[r,no head,double line] & x
    \end{tikzcd}
  \end{equation} 
\end{remark}
\begin{definition}
  Given a simplicial set $X$, two 1-simplices $f,g:x\to y$ are \emph{homotopic} if there is a 2-simplex of the form: 
  \begin{center}
    \begin{tikzcd}
      & y \arrow[dr,no head,double line] & \\
      x \arrow[ru,"f"] \arrow[rr,"g"'] & {} & y 
    \end{tikzcd}
  \end{center}
  Given 0-simplices $x,y$, denote by $\hom_{\Ho(X)}(x,y)$ the set of 1-simplices $x\to y$ modulo the equivalence relation generated by being homotopic. Given a 1-simplex $f:x\to y$, its homotopy class in $\hom_{\Ho X}(x,y)$ is denoted $[f]$. 
\end{definition}
\begin{lemma}[{\cite{kerodon2026homcat}}]\label{lem:homcat}
  Let $X$ be an $\infty$-category, then: 
  \begin{enumerate}
    \item For every pair $x,y$ of 0-simplices, being homotopic is an equivalence relation on the set of 1-simplices $x\to y$. 
    \item For every pair $f:x\to y$ and $g:y\to z$, there is a 2-simplex of the form \begin{equation}\label{eq:comp}
      \begin{tikzcd}
        & y \arrow[dr,"g"] & \\
        x \arrow[ru,"f"] \arrow[rr,"h"'] & & z
      \end{tikzcd}
    \end{equation} 
    \item The homotopy class of $h$ in \cref{eq:comp} only depends on the homotopy classes of $f$ and $g$.
    \item For every triple $x,y,z$ of $0$-simplices, there is a composition law \begin{equation}
      \begin{tikzcd}
        \hom_{\Ho X}(x,y) \times \hom_{\Ho X}(y,z) \arrow[r,"\circ_{x,y,z}"] & \hom_{\Ho X}(x,z)
      \end{tikzcd}
    \end{equation}defined as follows: Given $f:x\to y,g:y\to z$, let $h$ be a 1-simplex as in \cref{eq:comp}, then $[g]\circ[f]:=[h]$. 
    \item The composition laws $\circ_{x,y,z}$ are associative. 
    \item Given a 0-simplex $x$, the left homotopy class of $s^0_0(x)$ acts as the left and right identity with respect to the composition laws above. 
  \end{enumerate}
\end{lemma}
\begin{definition}
  Let $X$ be a $\infty$-category, the \emph{homotopy category}, denoted $\Ho X$, is the category defined as follows: 
  \begin{enumerate}
    \item The set of objects is $X_0$.
    \item Given a pair of objects $x,y$, let $\hom_{\Ho X}(x,y)$ be the set of morphisms $x\to y$. 
    \item Take $\circ_{x,y,z}$ from \cref{lem:homcat} as composition laws.
  \end{enumerate} 
\end{definition}
\begin{definition}
  Let $X$ be a $\infty$-category, a 1-simplex $f:x\to y$ is an \emph{equivalence} if $[f]$ is an isomorphism in $\Ho X$.
\end{definition}
The following theorem shows that $\infty$-groupoids have a relation to $\infty$-categories similar to that of ordinary groupoids to ordinary categories. 
\begin{theorem}[\cite{kerodon2026joyal}]
  A quasi-category $X$ is a $\infty$-groupoid if and only if $\Ho X$ is a groupoid. 
\end{theorem}
$\infty$-groupoids naturally form a full sub-category of $\sset$. To construct the $\infty$-category of $\infty$-groupoids, we use the simplicial nerve of Lurie. 
\begin{definition}
  Denote by $\scat$ the category of simplicially enriched categories. A simplicially enriched category is called \emph{locally fibrant} if its hom-simplicial sets are $\infty$-groupoids.  
\end{definition}
Recall that $\sset$ is self-enriched as follows: 
\begin{definition}
   Given two simplicial sets $X,Y$, the \emph{hom-simplicial set} $\hom^\Delta_{\sset}(X,Y)$ is defined as follows: A $n$-simplex consists of a map of simplicial sets $\Delta^n\times X\to Y$. 
\end{definition}
\begin{lemma}\label{lem:functinfgrpd}
  If $X$ is a $\infty$-groupoid, then $\hom^\Delta_{\sset}(B,X)$ is a $\infty$-groupoid, for every simplicial set $B$. 
\end{lemma}
\begin{proof}
  Corollary of \cite{kerodon2026exponential} by taking $f$ the terminal map $X\to\Delta^0$ and $i$ the initial map $\emptyset\to B$. 
\end{proof}
\begin{definition}
  Let $(P,\leq)$ be a partially ordered set, denote by $\Path(P)$ the following simplicial category: 
  \begin{enumerate}
    \item Objects are the elements of $P$. 
    \item Given $x,y\in P$, let $[x,y]:=\{z\in P|x\leq z\leq y\}$ and $P_{x,y}$ the set of sub-sets $S\subseteq[x,y]$ that are finite, linearly ordered, and contain $\{x,y\}$. We order $P_{x,y}$ by reverse inclusion ($S\leq T$ if $S\supseteq T$). Finally, let $\hom_{\Path(P)}(x,y)$ be the nerve of $(P_{x,y},\supseteq)$. 
    \item Given $x,y,z\in P$, composition \begin{equation}
      \begin{tikzcd}
        \hom_{\Path(P)}(x,y)\times\hom_{\Path(P)}(y,z) \arrow[r] & \hom_{\Path(P)}(x,z)
      \end{tikzcd}
    \end{equation} is the nerve of the union map $\cup:P_{x,y}\times P_{y,z}\to P_{x,z}$. 
  \end{enumerate}
  Given a monotone map $f:P\to Q$, let $\Path(f):\Path(P)\to\Path(Q)$ denote the following functor: 
  \begin{enumerate}
    \item On objects, it is simply $f$.
    \item Given $x,y\in P$, define $\Path(f)$ as the nerve of the functor $f_*:P_{x,y}\to Q_{f(x),f(y)}$ given by taking direct images (i. e. $f_*(S)=f(S)$). 
  \end{enumerate}
Restricting to $\BDelta$, we obtain a cosimplicial simplicial category $\Path:\BDelta\to\scat$. 
\end{definition}
\begin{definition}
  Given a simplicial category $\lC$, its \emph{simplicial nerve} is the simplicial set $\mN_\Delta\lC$ defined as follows:  A $n$-simplex of $\mN_\Delta\lC$ consists of a functor $\Path_n:=\Path(\langle n\rangle)\to\lC$. 
\end{definition}
\begin{remark}$\Path_0$ and $\Path_1$ are the categories $\langle0\rangle$ and $\langle 1\rangle$ viewed as simplicially enriched categories with discrete hom-simplicial sets, therefore a functor $\Path_0\to\lC$, resp. $\Path_1\to\lC$, is determined by a single object, resp. 1-morphism. $\Path_2$ admits the following description:
\begin{enumerate}
    \item Its set of objects is $\langle2\rangle$.
    \item $P_{0,1}$ and $P_{1,2}$ are both singletons, hence $\hom_{\Path_2}(0,1)\cong\hom_{\Path_2}(1,2)\cong\Delta^0$. 
    \item $P_{0,2}=\{[0,2]\leq\{0,2\}\}$ (recall that $P_{i,j}$ is ordered by reversed inclusion), so $\hom_{\Path_2}(0,2)\cong\Delta^1$. Moreover, $[0,2]$ is the composition $\{1,2\}\circ\{0,1\}$.  
  \end{enumerate}
  We can conclude that a functor $\Path_2\to\lC$ is determined by the following data: A triple of 1-morphisms $f:x\to y,g:y\to z$, and $h:x\to y$, together with a 1-simplex $g\circ f\Rightarrow h$ in $\hom_{\lC}(x,z)$. 
\end{remark}
\begin{definition}
  Denote also by $\Path$ the functor $\sset\to\scat$ obtained by left Kan extension of $\Path:\BDelta\to\scat$. 
\end{definition}
\begin{theorem}
  The functor $\Path$ is left adjoint to $\mN_\Delta$ and form a Quillen equivalence between the \emph{Dwyer-Kan-Bergner} model structure on $\scat$ and the \emph{Joyal} model structure on $\sset$. The fibrant objects in the $\sset_\mathrm{Joyal}$, resp. $\scat_\mathrm{DKB}$, are $\infty$-categories, resp. locally fibrant categories. In particular, $\mN_\Delta\lC$ is a $\infty$-category if $\lC$ is locally fibrant.
\end{theorem}
By \cref{lem:functinfgrpd}, we know that the full sub-category $\infty\Grpd\subseteq\sset$ of $\infty$-groupoids is self-enriched, therefore we give the following definition.
\begin{definition}
  Denote by $\lS:=\mN_\Delta(\infty\Grpd)$ the \emph{$\infty$-category of $\infty$-groupoids}.
\end{definition}
\begin{remark}
  In view of \cite{kerodon2026topspc}, we will also use the term \emph{space} to mean $\infty$-groupoid. 
\end{remark}

\section{Basic constructions}

Recall that $\sset$ and $\infty\Grpd$ are self-enriched. Similar to \cref{lem:functinfgrpd}, we have the following: 
\begin{lemma}[\cite{kerodon2026funccat}]
  If $X$ is a $\infty$-category, then $\hom_{\sset}^\Delta(B,X)$ is a $\infty$-category, for every simplicial set $B$. 
\end{lemma}
\begin{definition}
  Given a $\infty$-category $X$ and simplicial set $B$, denote by $\Fun(B,X)$ the \emph{$\infty$-category of functors} $\hom_{\sset}^\Delta(B,X)$. 
\end{definition}
\begin{definition}
  Denote by $\op$ the following endo-functor of $\BDelta$: 
  \begin{enumerate}
    \item On objects,  $\op(\langle n\rangle)=\langle n\rangle$. 
    \item Given $f:\langle k\rangle\to\langle n\rangle$, let $\op(f):\langle k\rangle\to\langle n\rangle$ be the function $\op(f)(i)=n-f(k-i)$. 
  \end{enumerate}Given a simplicial set $X$, denote by $X^\op$ the pre-composition of $X$ with $\op$. 
\end{definition}
\begin{lemma}
  If $X$ is a $\infty$-category, $X^\op$ is also an $\infty$-category. 
\end{lemma}
\begin{definition}
  Given a $\infty$-category $X$, we call $X^\op$ the \emph{opposite $\infty$-category}.  
\end{definition}
\nrnote{Slice $\infty$-categories?}

\section{Accessible and Presentable Categories}

In general, a limit, resp. colimit, preserving functor need not have a left, resp. right, adjoint. Here we wish to introduce a rather large class of $\infty$-categories for which the previous statement holds. We begin by recalling the definition of locally presentable 1-categories. Let $\kappa$ denote a regular cardinal. 
\begin{definition}
  A category $\lI$ is \emph{$\kappa$-filtered} if, for every $\lJ$ with $<\kappa$ many morphisms, every diagram $\lJ\to\lI$ has a cocone. A functor $F:\lC \to \lD$ is \emph{$\kappa$-accessible} if it preserves $\kappa$-filtered colimits. Given a category $\lC$, an object $X$ is \emph{$\kappa$-compact} if $\hom_{\lC}(X,-):\lC\to\set$ is $\kappa$-accessible. 
\end{definition}
\begin{definition}
  A category $\lC$ is \emph{$\kappa$-accessible} if there exists a set $S\subseteq\lC_0$ of $\kappa$-compact objects that generate $\lC$ under $\kappa$-filtered colimits. A category is \emph{accessible} if it is $\kappa$-accessible, for some regular cardinal $\kappa$. 
\end{definition}
\begin{definition}
  A category $\lC$ that is accessible and cocomplete is called \emph{locally presentable}.
\end{definition}
\begin{theorem}
  Let $\lC$ be a category, then $\lC$ is locally presentable if and only if there exists a small category $S$ such that the induced functor $\lC\to\lP(S)$ is a fully faithful, accessible right adjoint. 
\end{theorem}
\begin{theorem}
  Let $\lC,\lD$ be locally presentable categories. A functor $F\colon \lC \to \lD$ is a left, resp. right, adjoint if and only if it preserves colimits, resp. it preserves limits and is accessible.
\end{theorem}
\begin{definition}
  Let $X$ be a $\infty$-category. The \emph{$\infty$-category of pre-sheaves of spaces} is defined as $\lP(X):=\hom_{\sset}(X^{\op},\lS)$.
\end{definition}
\begin{theorem}[Yoneda]
  Given a $\infty$-category $X$, there is a fully faithful functor $y:X\to\lP(X)$, called the \emph{Yoneda embedding}, such that: Given a cocomplete $\infty$-category $Y$, pre-composition by $y$ induces an equivalence \begin{equation}
    \begin{tikzcd}
      \Fun^\mL(\lP(X),Y) \arrow[r] & \Fun(X,Y)
    \end{tikzcd}
  \end{equation}where $\Fun^\mL$ denotes the category of colimit preserving functors. 
\end{theorem} The definition of accessible category transfers directly to the $\infty$-categorical setting. 
\begin{theorem}\label{thm:locpresquasi}
  A $\infty$-category $X$ is locally presentable (cocomplete and accessible) if and only if there is a small sub-$\infty$-category $S$ such that $X\to\Fun(S^\op,\lS)$ is a fully faithful, accessible right adjoint. 
\end{theorem}
\begin{remark}
  In view of \cref{thm:locpresquasi}, one can define a category to be \emph{locally presentable} if it is the accessible right localization of a pre-sheaf category for some small $\infty$-category $S$. In particular, every pre-sheaf category is locally presentable. 
\end{remark}
\begin{theorem}
  Let $X,Y$ be presentable $\infty$-categories, then a functor $f:X\to Y$ is a left, resp. right, adjoint if and only if it preserves colimits, resp. it preserves limits and is accessible.
\end{theorem}
\section{Stable \texorpdfstring{$\infty$}{oo}-Categories and Spectra}
We now use the $\infty$-categorical framework to study spectra. Here are some result that justify the study of spectra. 
\nrnote{Examples of stable phenomena? Freudenthal's suspension theorem, Alexander duality of manifolds, etc.}
\begin{definition}
  Let $\lC$ be an $\infty$-category, an object $0$ that is both initial and terminal is called 
  \emph{zero object}. A category $\lC$ with a zero object is called a \emph{pointed category}.
\end{definition}
\begin{example}
  Let $1\in\lC$ be a terminal object, then the identity of $1$ is the zero object in the slice category $\lC_{1/}$ of objects under $1$. In particular, the category $\lS_*=\lS_{*/}$ of pointed spaces is pointed. 
\end{example}
\begin{proposition}
  Let $\lD$ be a pointed $\infty$-category. Evaluation at the 0-sphere $S^0$ induces an equivalence \begin{equation}
    \begin{tikzcd}
      \Fun^\mL(\lS_*,\lC) \arrow[r] & \lC
    \end{tikzcd}
  \end{equation}
\end{proposition}
We now introduce the notion of a {triangle}.
\begin{definition}
  Let $\lC$ be a pointed $\infty$-category. A \emph{triangle} in $\lC$ is a commutative diagram of the form \begin{equation}\label{eq:triangle}
    \begin{tikzcd}
      X \arrow[r] \arrow[d] & Y \arrow[d] \\
      0 \arrow[r] & Z
    \end{tikzcd}
  \end{equation}A triangle is \emph{exact}, resp. \emph{coexact}, if it is a pullback, resp. pushout, square. 
\end{definition}
\begin{definition}
  Let $\lC$ be a pointed $\infty$-category. Denote by $\lC^{\Sigma}$, resp. $\lC^\Omega$, the full sub-category of $\Fun(\Delta^1\times\Delta^1,\lC)$ of coexact, resp. exact, triangles of the form 
  \begin{equation}\label{eq:exact}
  \begin{tikzcd}
   X \arrow[r]  \arrow[d] & 0 \arrow[d] \\ 
   0 \arrow[r] & Y
  \end{tikzcd},
\end{equation}
\end{definition}
If $\lC$ is finitely cocomplete, resp. complete, for every object $X$, resp. $Y$, there is a contractible space of coexact, resp. exact, triangles as \cref{eq:exact}. In particular, $\lC\simeq\lC^\Sigma$ and $\lC\simeq\lC^\Omega$.  
\begin{proposition}
  If $\lC$ is a finitely complete and cocomplete pointed $\infty$-category, define the following functors Then the functors
  \begin{equation}
    \begin{tikzcd}
      \Sigma:\lC \arrow[r] & \lC^\Sigma \arrow[r,"\mathrm{ev}_{(1,1)}"] & \lC  & & \Omega:\lC \arrow[r] & \lC^\Omega \arrow[r,"\mathrm{ev}_{(0,0)}"] & \lC
    \end{tikzcd}
  \end{equation}are adjoint ($\Sigma$ is left adjoint to $\Omega$). 
\end{proposition}

\begin{theorem}\label{thm:stable}
  Let $\lC$ be a finitely bicomplete pointed $\infty$-category. The following are equivalent:
  \begin{enumerate}
    \item A triangle is exact if and only if it is coexact. 
    \item $(\Sigma,\Omega)$ is an adjoint equivalence.
    \item A commutative square is a pullback if and only if it is a pushout. 
  \end{enumerate}
\end{theorem}
\begin{definition}
  A finite bicomplete pointed $\infty$-category $\lC$ satisfying any of the equivalent conditions in \cref{thm:stable} is called \emph{stable}.
\end{definition}
If $\bA$ denotes a nice abelian category, there is a \emph{derived $\infty$-category} of $\bA$, denoted $\lD(\bA)$ such that $\Ho\lD(\bA)=D(\bA)$ is the ordinary derived category of $\bA$, i.e. the localization of chain complex at quasi-isomorphisms. From homological algebra, it is known that $D(\bA)$ underlies the structure of a triangulated category, which turns out to be the 1-categorical reflection of $\lD(\bA)$ being stable. 
\begin{proposition}[{\cite[3.11]{lurie2017ha}}]
  If $\lC$ is a stable $\infty$-category, then $\Ho\lC$ has a canonical structure of a triangulated category. 
\end{proposition}To construct the stabilization of a pointed $\infty$-category, there are several approaches, such as reduced excisive functors on $\lS^\mathrm{fin}_*$, the category of pointed, finite spaces, see \cite[1.4.2.8]{lurie2017ha}. Here we consider the more explicit approach using spectrum objects.
\begin{definition}
  Let $\lC$ be a pointed $\infty$-category. A \emph{pre-spectrum object in $C$} consists of a functor $E:\bZ\times\bZ\to\lC$ such that $E(n,m)\simeq0$, for all $n\neq m$. Denote by $\PSp(\lC)$ the category of pre-spectrum objects. The functor $\Omega^{\infty-n}:\PSp(\lC)\to\lC$ is defined as evaluation at $(n,n)$. 
\end{definition}
For every $n$, the diagram \begin{equation}
  \begin{tikzcd}
    E(n,n) \arrow[r]\arrow[d] & 0 \arrow[d] \\
    0 \arrow[r] & E(n+1,n+1) 
  \end{tikzcd}
\end{equation}determines a pair of adjoint morphisms \[\alpha_n:\Sigma E(n,n)\to E(n+1,n+1),\qquad\beta_n:E(n,n)\to\Omega E(n+1,n+1)\]
\begin{definition}
  Let $\lC$ be a pointed $\infty$-category. A \emph{spectrum object in $\lC$} consists of a pre-spectrum object $E$ such that $\beta_n$ is an equivalence, for all $n$. Denote by $\Sp(\lC)\subseteq\PSp(\lC)$ the full sub-category of spectrum objects. 
\end{definition}
\begin{theorem}
  Let $\lC$ be a presentable pointed $\infty$-category, then $\Omega^{\infty-n}:\Sp(\lC)\to\lC$ admits a left adjoint $\Sigma^{\infty-n}:\lC\to\Sp(\lC)$, for every $n$. 
\end{theorem}
In particular, $\Sigma^\infty:\lC\to\Sp(\lC)$ has the following universal property. 
\begin{theorem}
 Let $\lC$ be a presentable pointed $\infty$-category. Given a stable $\infty$-category $\lD$, pre-composition by $\Sigma^\infty$ induces an equivalence 
 \begin{equation}
  \begin{tikzcd}
    \Fun^\mL(\Sp(\lC),\lD) \arrow[r] & \Fun^\mL(\lC,\lD)
  \end{tikzcd}
 \end{equation}In particular, for $\lC=\lS_*$, evaluation at the \emph{sphere spectrum} $\bS=\Sigma^\infty S^0$ induces an equivalence
 \begin{equation}
  \begin{tikzcd}
    \Fun^\mL(\Sp(\lS_*),\lD) \arrow[r] & \lD
  \end{tikzcd}
 \end{equation}
\end{theorem}
\begin{definition}
  The \emph{$\infty$-category of spectra} is the category of spectrum objects in pointed spaces. 
\end{definition}

\section{Generalized Cohomology Theories}

We shall now use the language of $\infty$-categories to reformulate the concept of generalized cohomology theory \` a-l\`a Eilenberg-Steenrod. In this new context, we recall a representability theorem for cohomology theories by spectrum object. 
\begin{remark}
  Denote by $\set^\bZ$ the category of $\bZ$-indexes families of sets. Given an object $S$ and $n\in\bZ$, denote by $\Sigma^n S$ the shifted family $(\Sigma^nS)_i=S_{i-n}$.  
\end{remark}
\begin{definition}[{\cite[1.4.1.6]{lurie2017ha}}]\label{def:cohthe}
  Let $\lC$ be a finitely cocomplete pointed $\infty$-category, $\Sigma_\lC:\lC \to \lC$ the induced suspension functor. A \emph{generalized cohomology theory} is a functor $H:\Ho\lC^{\op}\to\set^\bZ$ together with a natural isomorphism $\partial:\Sigma H\to H\Sigma_\lC$ such that:
  \begin{itemize}
    \item $H$ preserves arbitrary products. In particular, $H^n(0)$ is the one-point set. Given an object $X$, the unique morphism $X\to0$ induces an element $*\simeq H^n(0)\to H^n(X)$, which we denote by $0$. 
    \item Given a coexact triangle $X'\to X\to X''$, if $\eta\in H^n(X)$ has image $0\in H^n(X'')$, then it lies in the image of $H^n(X')\to H^n(X)$. 
  \end{itemize}
\end{definition}
\begin{theorem}[{\cite[1.4.1.10]{lurie2017ha}}]
 Let $\lC$ be a nice $\infty$-category and $(H,\partial)$ a generalized cohomology theory, then, for every $n$, the functor $H^n$ is representable by an object $E(n)$. 
\end{theorem}
The natural isomorphism $\partial$ translates into an equivalence $E(n)\simeq\Omega E(n+1)$, which is then used to construct a spectrum object representing the cohomology theory $H^n$, see \cite[1.4.1.11]{lurie2017ha}.
\begin{remark}
  For $\lC=\lS_*$, the above definition of cohomology theory reduces to the classical Eilenberg-Steenrod definition. Since $\lS_*$ is nice, we thus recover the classical \emph{Brown representability theorem}. 
\end{remark}

{\footnotesize
\bibliographystyle{alpha}
\bibliography{main}
}
\end{document}